{\LARGE Model Selection for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-01-28 Paper/main.tex
Equation Simplification

	\begin{equation}\label{FPCA_basis_expansion}
		\begin{split}
			\hat{\xi}_{j, i} & = \int_{0}^{1} \left({\color{red} f_i(s) - \hat{\mu}(s)}\right) {\color{blue}\hat{\nu}(s)} \mathrm{d}s
			= \int_{0}^{1} \left({\color{red}\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)}\right) \left({\color{blue}\sum_{k \in \mathcal{L}} b_{k} \psi_{k}(s)}\right) \mathrm{d}s \\
			& = \sum_{j \in \mathcal{I}}\sum_{k \in \mathcal{L}} {\color{teal} a_{i,j} b_{k} \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s}
			= \sum_{j \in \mathcal{I}} \sum_{k \in \mathcal{L}} {\color{teal} Z_{i,j,k}} 
			\approx \sum_{j = 1}^{J} {\color{violet}\sum_{k = 1}^{K} Z_{i,j,k}} 
			= \sum_{j = 1}^{J} {\color{violet}\tilde{Z}_{i,j}}
		\end{split}
	\end{equation}

@@

	\begin{equation}
		\begin{split}
			Z_{i, j, k} & =  a_{i,j} b_k \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \quad j = 1, \dots, L \quad k = 1, \dots, L \\
			\tilde{Z}_{i, j}& = a_{i,j} \sum_{k = 1}^{L} \left[ b_k \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \right] \quad j = 1, \dots, L
		\end{split}
	\end{equation}

>>>>

	\begin{equation}\label{FPCA_basis_expansion}
		\begin{split}
			\hat{\xi}_{i}^m & = \int_{0}^{1} \left({\color{red} f_i(s) - \hat{\mu}(s)}\right) {\color{blue}\hat{\nu}^m(s)} \mathrm{d}s
			= \int_{0}^{1} \left({\color{red}\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)}\right) \left({\color{blue}\sum_{k \in \mathcal{L}} b_{k}^m \psi_{k}(s)}\right) \mathrm{d}s \\
			& = \sum_{j \in \mathcal{I}} \left[ a_{i,j}\sum_{k \in \mathcal{L}} {\color{teal}  b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s}\right]
			= \sum_{j \in \mathcal{I}} \left[a_{i,j}\sum_{k \in \mathcal{L}} {\color{teal} Z_{j,k}^m} \right]
			\approx \sum_{j = 1}^{J} \left[a_{i,j}{\color{violet}\sum_{k = 1}^{K} Z_{j,k}^m} \right]
			= \sum_{j = 1}^{J} a_{i,j}{\color{violet}\tilde{Z}_{j}^m}
		\end{split}
	\end{equation}

@@

	\begin{equation}
		\begin{split}
			Z_{j, k}^m & =  b_{k}^m \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \quad j = 1, \dots, L \quad k = 1, \dots, L \\
			\tilde{Z}_{j}^m& = \sum_{k = 1}^{L} \left[ b_k^m \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \right] \quad j = 1, \dots, L
		\end{split}
	\end{equation}
